### 2020-05-26 manuscript/manuscript.rmd
add Whelan2017_strict.phy_Poisson_CAT70.bpdiff

To advance this problem it is therefore critical to synthesize published results and explore variation in a standardized framework. Here, we synthesize data and results from previous phylogenomic analyses that tested Ctenophora-sister and Porifera-sister from 13 studies (Table 1). These matrices include all relevant studies published before 2020 for which we could obtain data matrices with gene partition annotations.

@@

The published analyses considered here differ in a variety of ways, including the model of molecular evolution, gene selection, ingroup species selection, and outgroup species selection.

>>>>

To advance this problem it is therefore critical to synthesize published results and explore variation in a standardized and systematic framework. Here, we synthesize data and results from previous phylogenomic analyses that tested Ctenophora-sister and Porifera-sister from 13 studies (Table 1). These matrices include all relevant studies published before 2020 for which we could obtain data matrices with gene partition annotations.

@@

The published analyses considered here differ in a variety of ways, including the model of molecular evolution, gene selection, and ingroup and outgroup species selection.
